TBD

### 2023-03-31 outputs/paper/timesheet_analysis.qmd
Populated README & clean up file names

cleaned_time_sheet = read_csv(
  file = here("outputs/data/cleaned_time_sheet.csv"),
  show_col_types = FALSE
)

# set factor
cleaned_time_sheet$type =
  factor(cleaned_time_sheet$type,
         levels = c(
           "Research",
           "Course Work",
           "TA",
           "Admin",
           "Learning",
           "Other Activities"
         )
  )
```

@@

# Calculate data for hours of each day
hourly_calc <- 
  cleaned_time_sheet |>
  slice(rep(1:n(), each = 24)) |>
  mutate(hour_value = rep(0:23, times = nrow(cleaned_time_sheet))) |>
  mutate(
    worked = (start_date == end_date & 
                hour(start_time) <= hour_value & 
                convert_hms_to_hours(end_time) > hour_value
              ) |
              (start_date < end_date & 
                 (convert_hms_to_hours(end_time) > hour_value |
                    hour(start_time) <= hour_value)
               )
    ) |>
  filter(worked) |>
  select(-worked)
```

@@

generate_compare_bar_graph(
  ggplot_data = 
    cleaned_time_sheet |>
    filter(type == "Course Work") |>
    group_by(project) |>
    summarize(effort = sum(effort_hours)) |>
    ggplot(aes(x = factor(project, 
                          level = c("INF2241", "INF3104", "INF3001", "INF2169")), 
               y = effort)),
  position = "identity",
  xlabel = "Course",
  ylabel = "Effort (hours)"
) +
  geom_text(aes(label = round(effort, 0)), vjust = -0.2) +
  ylim(0, 145)
```

@@

generate_compare_bar_graph(
  ggplot_data = 
    cleaned_time_sheet |>
    filter(type %in% c("TA", "Research", "Course Work", "Learning")) |>
    mutate(effort_bin = case_when(
      effort_hours < 1 ~ "< 1",
      effort_hours >= 1 & effort_hours < 2 ~ "1 - 2",
      effort_hours >= 2 & effort_hours < 3 ~ "2 - 3",
      effort_hours >= 3 & effort_hours < 4 ~ "3 - 4",
      effort_hours >= 4 & effort_hours < 5 ~ "4 - 5",
      effort_hours >= 5 ~ "> 5"
    )) |>
    group_by(effort_bin, type) |>
    count() |>
    ungroup() |>
    mutate(pct = n / sum(n)) |>
    ggplot(aes(x = factor(effort_bin, 
                          level = c("< 1", "1 - 2", "2 - 3", "3 - 4", "4 - 5", "> 5")), 
               y = pct, 
               fill = type)),
  position = "stack",
  yscale = scales::percent,
  xlabel = "Length of session (in hours)",
  ylabel = "Percentage of occurrence"
)

@@

cleaned_time_sheet |>
  filter(effort_hours > 4) |>
  group_by(type) |>
  summarize(
    count = n(),
    avg_effort = mean(effort_hours),
    max_effort = max(effort_hours)
  ) |>
  mutate(work_performed = c(
    "data analysis, paper writing, paper review",
    "assignments from INF2241, INF3104",
    "CCT419 (UX and board games) marking",
    "NSERC application, SRI scholarship",
    "Critical Computing - qualitative analysis workshop",
    "Data Science Hackathon, update resume"
  )) |>
  arrange(type, desc(count)) |>
  kable(
    booktabs = TRUE,
    digits = 1,
    linesep = "",
    align = 'lcccl',
    col.names = c("Type", "Count", "Avg Effort", "Max Effort" ,"Tasks")
  )
```

@@

tmp_daily <- merge(tmp_daily_effort, tmp_daily_projects, by="start_date")
rm(tmp_daily_effort)
rm(tmp_daily_projects)

tibble(
  Statistics = c("Mean", "SD", "Min", "Max"),
  "Hours Worked" = c(mean(tmp_daily$effort),
                     sd(tmp_daily$effort),
                     min(tmp_daily$effort),
                     max(tmp_daily$effort)),
  "Number of Projects" = c(as.integer(mean(tmp_daily$projects)),
                           as.integer(sd(tmp_daily$projects)),
                           as.integer(min(tmp_daily$projects)),
                           as.integer(max(tmp_daily$projects))),
) |>
  kable(
    booktabs = TRUE,
    digits = 1,
    align = 'c'
  )
```

@@

predict_completion_date(
  calibrate_model(as.Date("2023-01-09"), as.Date("2023-03-30"), "Course Work"),
  start_date = as.Date("2023-03-31"),
  effort_hours = 10,
  pct_effort = 0.5, 
  include_weekends = FALSE)$schedule |>
  kable(
    booktabs = TRUE,
    linesep = ""
  )
```

@@

Shiny App

![](shiny_app_screenshot.png)

>>>>

cleaned_time_sheet <- read_csv(
  file = here("outputs/data/cleaned_time_sheet.csv"),
  show_col_types = FALSE
)

# set factor
cleaned_time_sheet$type <-
  factor(cleaned_time_sheet$type,
         levels = c(
           "Research",
           "Course Work",
           "TA",
           "Admin",
           "Learning",
           "Other Activities"
         )
  )
```

@@

# Calculate data for hours of each day
hourly_calc <-
  cleaned_time_sheet |>
  slice(rep(seq_len(n()), each = 24)) |>
  mutate(hour_value = rep(0:23, times = nrow(cleaned_time_sheet))) |>
  mutate(
    worked = (start_date == end_date &
                hour(start_time) <= hour_value &
                convert_hms_to_hours(end_time) > hour_value
              ) |
              (start_date < end_date &
                 (convert_hms_to_hours(end_time) > hour_value |
                    hour(start_time) <= hour_value)
               )
    ) |>
  filter(worked) |>
  select(-worked)
```

@@

generate_compare_bar_graph(
  ggplot_data =
    cleaned_time_sheet |>
    filter(type == "Course Work") |>
    group_by(project) |>
    summarize(effort = sum(effort_hours)) |>
    ggplot(aes(x = factor(
                      project,
                      level = c("INF2241", "INF3104", "INF3001", "INF2169")),
               y = effort)),
  position = "identity",
  xlabel = "Course",
  ylabel = "Effort (hours)"
) +
  geom_text(aes(label = round(effort, 0)), vjust = -0.2) +
  ylim(0, 145)
```

@@

generate_compare_bar_graph(
  ggplot_data =
    cleaned_time_sheet |>
    filter(type %in% c("TA", "Research", "Course Work", "Learning")) |>
    mutate(effort_bin = case_when(
      effort_hours < 1 ~ "< 1",
      effort_hours >= 1 & effort_hours < 2 ~ "1 - 2",
      effort_hours >= 2 & effort_hours < 3 ~ "2 - 3",
      effort_hours >= 3 & effort_hours < 4 ~ "3 - 4",
      effort_hours >= 4 & effort_hours < 5 ~ "4 - 5",
      effort_hours >= 5 ~ "> 5"
    )) |>
    group_by(effort_bin, type) |>
    count() |>
    ungroup() |>
    mutate(pct = n / sum(n)) |>
    ggplot(aes(x = factor(
                    effort_bin,
                    level = c("< 1", "1 - 2", "2 - 3", "3 - 4", "4 - 5", "> 5")),
               y = pct,
               fill = type)),
  position = "stack",
  yscale = scales::percent,
  xlabel = "Length of session (in hours)",
  ylabel = "Percentage of occurrence"
)

@@

cleaned_time_sheet |>
  filter(effort_hours > 4) |>
  group_by(type) |>
  summarize(
    count = n(),
    avg_effort = mean(effort_hours),
    max_effort = max(effort_hours)
  ) |>
  mutate(work_performed = c(
    "data analysis, paper writing, paper review",
    "assignments from INF2241, INF3104",
    "CCT419 (UX and board games) marking",
    "NSERC application, SRI scholarship",
    "Critical Computing - qualitative analysis workshop",
    "Data Science Hackathon, update resume"
  )) |>
  arrange(type, desc(count)) |>
  kable(
    booktabs = TRUE,
    digits = 1,
    linesep = "",
    align = "lcccl",
    col.names = c("Type", "Count", "Avg Effort", "Max Effort", "Tasks")
  )
```

@@

tmp_daily <- merge(tmp_daily_effort, tmp_daily_projects, by = "start_date")
rm(tmp_daily_effort)
rm(tmp_daily_projects)

tibble(
  Statistics = c("Mean", "SD", "Min", "Max"),
  "Hours Worked" = c(mean(tmp_daily$effort),
                     sd(tmp_daily$effort),
                     min(tmp_daily$effort),
                     max(tmp_daily$effort)),
  "Number of Projects" = c(as.integer(mean(tmp_daily$projects)),
                           as.integer(sd(tmp_daily$projects)),
                           as.integer(min(tmp_daily$projects)),
                           as.integer(max(tmp_daily$projects))),
) |>
  kable(
    booktabs = TRUE,
    digits = 1,
    align = "c"
  )
```

@@

predict_completion_date(
  calibrate_model(as.Date("2023-01-09"), as.Date("2023-03-30"), "Course Work"),
  start_date = as.Date("2023-03-31"),
  effort_hours = 10,
  pct_effort = 0.5,
  include_weekends = FALSE)$schedule |>
  kable(
    booktabs = TRUE,
    digits = 1,
    linesep = ""
  )
```

@@

See @fig-app-screenshot for a snapshot of the Shiny application.

![Screenshot of the application for prediction models](shiny_app_screenshot.png){#fig-app-screenshot}
